X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on a conventional source

### 2013-10-31 point_by_point_response.tex

In order to address the concerns of reviewer \#1, the short review of the
previous results in the
introductory paragraph has been updated:
\begin{quote}
The vast majority of phase-sensitive techniques, including crystal analyzer based [5, 6] or
interferometric [7, 8] methods rely on X-ray beams of high spatial and temporal coherence,
which is available only at synchrotron sources. Inline phase contrast [9–11] and Talbot interferometry [12–14] need high spatial coherence but are available on polychromatic microfocus
sources. Phase-contrast imaging using X-ray beams of low temporal and spatial coherence
such as conventional low-brilliance X-ray tubes have been demonstrated with coded apertures [15] and Talbot-Lau interferometry [16]. Analyzer-based systems have been recently
extended to tube sources [17, 18] but only at energies up to the tungsten
$K_\alpha$ line at 60 keV. In
addition to phase sensitivity, analyzer-based and Talbot interferometry also provide (with different retrieval mechanisms) information about the integrated
local small angle scattering power from microscopic density fluctuations in a specimen [19].
This signal is known under the name of dark-field, scatter or visibility reduction contrast.
High-energy Talbot interferometry has been reported so far using a synchrotron source
at nominal energies of 82 keV [20] and 123 keV [21]. Using a low-brilliance X-ray tube,
Talbot-Lau interferometry was applied so far at 60 keV mean energy [22]. Medical imaging
applications may benefit from phase contrast at higher energies: chest or abdominal radiography or CT require an acceleration voltage between 100 and 150 kVp. Other potential applications are
homeland security or chip failure analysis, which require high energies for the visualization
of materials of high density and atomic number.
\end{quote}

\begin{reviewerquote}
    Furthermore, the authors mention that the results in Fig. 3 show the benefit of the phase nature of the image, but I think that the authors should provide a more detailed explanation about the contrasts in the images because the contrast of soldering points underneath the resistors should not be reduced in the differential attenuation image for monochromatic x-rays. The authors should explain quantitatively why the contrast is reduced. Otherwise, the authors' assertion is suspicious.
\end{reviewerquote}
A paragraph has been added to discuss the different beam hardening behaviour of
the absorption and differential phase image:
\begin{quote}
In the attenuation image, the contrast of the soldering points of the integrated circuit is reduced underneath the
resistors, while in the phase image, they can clearly be identified. The reduced contrast
of the soldering points in the absorption image is due to beam hardening. The spectrum
impinging on these soldering point is hardened by the resistors in the upper layer, resulting
in lower absorption contrast. Due to the weaker energy dependency of phase
shifts ($1/E$
compared to $1/E^3$), phase-contrast images are less sensitive to beam hardening [31], which
explains the lower contrast reduction of the soldering points underneath the resistors in the
phase image of the chip. This result shows the benefit of the phase contrast in high-energy
X-ray imaging, which may be useful to identify flaws in multilayered structures such as
electronic chips.
\end{quote}

\section*{Reviewer \#2}
\begin{reviewerquote}
    However, this solution comes with significant drawbacks in terms of very
    limited fields of view~\SI{3}{\centi\metre} horizontally, a single detector pixel in the vertical direction), which at the moment seem hard to overcome.
\end{reviewerquote}
There is no fundamental limitation on the horizontal field of view in our
approach. On the contrary, our solution actually solves precisely this
issue, by easily matching the spherical wave front with the curved
structures.
Our approach removes any limitation to the horizontal field of view which would arise due to the large beam divergence. In addition, curved gratings can be easily stitched to cover an even larger field of view, if necessary.

With our scanning solution, the limitation of the vertical field of view does not come at the expense of
an increased dose. 
A similar scanning technique is already commercially offered in X-ray
mammography systems, like the MicroDose instrument of Philips, with a
significant reduction of the scattered radiation. We discussed this issue and
amended the text accordingly.
\begin{quote}
 Radiographic 2D imaging can be obtained by scanning the sample or a
thin fan beam. The scanning technique has been demonstrated to deliver less dose than the
conventional approach based on the illumination of a large area. In digital mammography,
for instance, where dose is a critical issue, Philips’ MicroDose system combines a scanning
approach with an highly collimated fan beam [27]. Thanks to the high collimation, the dose
deposited on patients has been reported to be significantly lower than with other instruments
based on the illumination of a large area detector [28]. 
\end{quote}

\begin{reviewerquote}
    Moreover, in the methods section the authors talk of a
    \SI{5}{\percent} visibility, which is even lower than that of the quoted papers by Pfeiffer's group (refs 18, 19), which, at least nominally, reach even higher energies (123 keV). Hence, the reduction in field-of-view does not seem to be counterbalanced by significant improvements in visibility. This is also supported by the relatively poor quality of the differential phase image compared to the derivative of the absorption image, where the only advantage seems to be the visibility of the soldering points beneath the resistors (primarily due to the fact that these do not produce area contrast in the DPC image), while everywhere else the contrast of the differentiated absorption image seems to be higher.
\end{reviewerquote}
We would like to remind to the reviewer \#2 that our data have been obtained on
a commercially available X-ray tube, while the cited experiment of Pfeiffer's
et al. has been carried out at a third generation synchrotron source, where
notably unsurpassed beam conditions can be created which are far from what one
can expect in real life (i.e. with conventional X-ray tubes). And, even if one
would like to still carry out this (unfair) comparison, we should mention that
our experiment is the first measurement of its kind with the first generation
of gratings made according to our innovative design. Pfeiffer's team uses
gratings obtained after almost a decade of development and, despite this and
the use of a synchrotron, they are not really further than us while they still
carry the intrinsic limitation of a limited grating height. We are well aware
that the quality of our images has still to be improved, but here we are
presenting the first experiments with edge-on grating illumination: we describe
its great potential but also mention its (temporary) limitations.
\begin{reviewerquote}
Finally, the novelty of the result is diminished by previous demonstrations that high energies in phase-contrast x-ray imaging could be reached by other methods (e.g. Ignatyev et al JAP 110 (2011) 014906), albeit in that case image quality seems to be lower.     
\end{reviewerquote}
Reviewer \#2 admits that in comparison with a coded-aperture based experiment at 100 kVp (Ignatyev et al.) our images (taken at 160 kVp) are better, which we of course appreciate.

### 2013-10-31 hedpc_natphys.tex
response and paper typos

High-energy Talbot interferometry has been reported so far using a
synchrotron source at nominal energies of
$\SI{82}{\kilo\electronvolt}$~\cite{Willner2013} and 
$\SI{123}{\kilo\electronvolt}$~\cite{Ruiz2013}.
Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
applied so far at $\SI{60}{\kilo\electronvolt}$ mean energy~\cite{Donath2009}.
Medical imaging applications may benefit from phase contrast at higher
energies: chest or abdominal
radiography or \ac{CT} require energies between $100$ and
$\SI{150}{\kilo\voltpeak}$. Other potential applications are homeland
security or chip failure analysis, which require high energies for the
visualization of materials of high density and atomic number.

@@

Increasing the aspect ratio of the gratings typically leads to a
reduction of the field of view due to the change of the grating transmission
function at high incident angles. In order to overcome this problem, the grating lines are circularly aligned 
with a radius equal to the distance to the source. This cannot be done with
the glancing angle approach~\cite{Stutman2012a}, and allows an arbitrarily
large field-of-view in a fan beam geometry.

The combination of edge-on illumination and circularly aligned structures
enables phase-contrast imaging at arbitrary design energies and with a
maximum field of view in the horizontal direction ($x$ direction). These
advantages come at the expense of a limited field of view in the vertical
direction ($y$ direction), which is, depending on the X-ray detector,
typically a few pixels. 
Radiographic 2D imaging can be obtained by scanning the sample or a thin fan
beam. The scanning technique has been demonstrated to deliver less dose than
the conventional approach based on the illumination of a large area. In
digital mammography, for instance, where dose is a critical issue, Philips'
MicroDose system combines a scanning approach with an highly collimated fan
beam~\cite{Aslund2007}. Thanks to the high collimation, the dose deposited
on  patients has been reported to be significantly lower than with other
instruments based on the illumination of a large area
detector~\cite{Oduko2010}.
Similarly, for tomographic images,
the approach allows single slice \ac{CT} or full 3D imaging in scanning mode.

>>>>

High-energy Talbot interferometry has been reported so far using a
synchrotron source at nominal energies of
$\SI{82}{\kilo\electronvolt}$~\cite{Willner2013} and 
$\SI{123}{\kilo\electronvolt}$~\cite{Ruiz2013}.
Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
applied so far at $\SI{60}{\kilo\electronvolt}$ mean energy~\cite{Donath2009}.
Medical imaging applications may benefit from phase contrast at higher
energies: chest or abdominal
radiography or \ac{CT} require an acceleration voltage between \num{100} and
$\SI{150}{\kilo\voltpeak}$. Other potential applications are homeland
security or chip failure analysis, which require high energies for the
visualization of materials of high density and atomic number.

@@

Increasing the aspect ratio of the gratings typically leads to a
reduction of the field of view due to the change of the grating transmission
function at high incident angles. In order to overcome this problem, the grating lines are circularly aligned 
with a radius equal to the distance to the source. 
This allows to achieve an arbitrarily large field of view in a fan-beam
geometry, a significant improvement compared to face-on based and glancing
angle~\cite{Stutman2012a} approaches.

The combination of edge-on illumination and circularly aligned structures
enables phase-contrast imaging at arbitrary design energies and with a
maximum field of view in the horizontal direction ($x$ direction). These
advantages come at the expense of a limited field of view in the vertical
direction ($y$ direction), which is, depending on the X-ray detector,
typically a few pixels. 
However, radiographic 2D imaging can be obtained by scanning the sample or a thin fan
beam. The scanning technique has been demonstrated to deliver less dose than
the conventional approach based on the illumination of a large area. In
digital mammography, for instance, where dose is a critical issue, Philips'
MicroDose system combines a scanning approach with an highly collimated fan
beam~\cite{Aslund2007}. Thanks to the high collimation, the dose deposited
on  patients has been reported to be significantly lower than with other
instruments based on the illumination of a large area
detector~\cite{Oduko2010}.
Similarly, for tomographic images,
the approach allows single slice \ac{CT} or full 3D imaging in scanning mode.
